### 2023-03-10 paper.tex
Write about palm-e

\subsection{Toolformer}
Transformers are able to produce very natural text but they struggle with seemingly
simple tasks such as simple mathematical calculations and factual information gathering.
To get around of these limitations, transformers can be taught to use external tools
to offload these tasks to applications better suited to them. \cite{schick_toolformer_2023} 
This can be achieved using additional fine tuning, as is the case with Toolformer
\cite{schick_toolformer_2023}, or by using few-shot methods telling the model 
about the tools available to it, as in Toolformer Zero \cite{markus_toolformer_2023}.

For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 
GPT-3.5 [citation needed], to do a simple calculation, it answers confidently. 
With a prompt of "\texttt{what is 491*397}" we receive a response of 
"\texttt{The product of 491 and 397 is 195127.}". Unfortunately, using a calculator
leads to a different answer: 194927. Dangerously close, but not quite there.

@@

\section{Problems}
TODO: write about hallucination, overconfidence, radicalization etc.

>>>>

\subsection{Toolformer}
Transformers are able to produce very natural text but as previously mentioned, they struggle with seemingly
simple tasks such as simple mathematical calculations and factual information gathering.
To get around of these limitations, transformers can be taught to use external tools
to offload these tasks to applications better suited to them. \cite{schick_toolformer_2023} 
This can be achieved using additional fine tuning, as is the case with Toolformer
\cite{schick_toolformer_2023}, or by using few-shot methods telling the model 
about the tools available to it, as in Toolformer Zero \cite{markus_toolformer_2023}.

\subsection{Multimodal Models}
Large language models have proven themselves very capable at a variety of language related
tasks. Their usefulness quickly diminishes the further we stray from their training set.
Using multimodal models (check name) however, we can widen the area of tasks the model
can complete and even achieve positive transfer, benefitting from the variety of tasks
it is trained for \cite{driess_palm-e_2023}.

PaLM-E is a multimodal language model utilizing a transformer based language model called
PaLM \cite{chowdhery_palm_2022,driess_palm-e_2023}. Multimodality refers to the fact that
the models accept types of input other than text. For example, PaLM-E accepts an input like
"\texttt{Q: What happened between <img\_1> and <img\_2>?}" \cite{driess_palm-e_2023} where
\texttt{<img\_1>} and \texttt{<img\_2>} refer to image embeddings. The E in PaLM-E refers to
the model being embodied. This means that the model is capable of performing tasks that
relate to real world objects. For example, the model can be used to plan high-level tasks
for a robot. \cite{driess_palm-e_2023}

\begin{figure}[h]
  \centering
  \includegraphics*[scale=0.1]{img/palm-e-transfer.png}
  \caption{
    PaLM-E displays positive transfer in learning. The performance is better for these three
    distinct robotics domains when trained together than when trained separately for the 
    specific tasks. \cite{driess_palm-e_2023}
  }
\end{figure}

\section{Problems}
TODO: write about hallucination, overconfidence, radicalization etc.
For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 
GPT-3.5 [citation needed], to do a simple calculation, it answers confidently. 
With a prompt of "\texttt{what is 491*397}" we receive a response of 
"\texttt{The product of 491 and 397 is 195127.}". Unfortunately, using a calculator
leads to a different answer: 194927. Dangerously close, but not quite there.

@@
